Notes on modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-06-18 docs/mvfits_paper/mvf.tex
updating docs, adding setup.py

    \State {\bf Input:} $ \{ \bf{x}, \bf{y}, $max\_degree = 6$, tol \}$

@@

      \State Select all symbols from $\mlam_{bulk}$ with degree less than or equal to current degree: $\mlam^{(d)}_{bulk}$
      \State Apply Alg. (\ref{alg:pgreedy}), \pgreedy{}, with $\mathcal{A}_{\gmvp{}}$ to get symbol subset, $\mlam^{(d)}_{opt}$ and estimator val, $\epsilon^{(d)}_{opt}$

@@

which is then fed back into \eqn{q:pinv3} for further refinement.

@@

\par With the conceptual tools in hand, we may proceed to constructing \gmvr{} be first defining its action, $\mathcal{A}_{\gmvr}$.

@@

@@

@@

@@

@@

    \State {\bf Input:} $ \{ \bf{x}, \bf{y} \}$

@@

    \State Define $\mathcal{A}_{\gmvp}$ as in Alg. (\ref{alg:A})
    \State Define, $\mlam_{bulk}$, bulk symbol space using the n-fold cartesian inner-product
    \State Define list of allowed polynomial degrees
    \For { $d_k$ in  }
      \State Select all numerator symbols with degree less than or equal to current
      \State Select all denominator symbols with degree less than or equal to current, enforcing no constant term
      \State Construct new symbol space by tagging each polynomial symbol with a boolean denoting whether it is in the numerator or denominator
      \State Apply \pgreedy{} to get the optimal symbol subset, $\mlam_{opt}$, and estimator value, $\epsilon_{opt}$.
      \If  { estimator has stalled }
        \State Break

@@

    \State Apply negative greedy to get final model

@@

    \State {\bf Output:} Final model

@@

%
\section{Results}
\label{results}

% Equations for QNM frequency fits
\begin{widetext}
	\input{src/cwfit_eqns}
\end{widetext}

>>>>

    \State {\bf Input:} $ \{ x, f, $max\_degree = 6$, tol \}$

@@

      \State Define $\mlam_{bulk}^{(d)}$ as all symbols from $\mlam_{bulk}$ with degree less than or equal to current degree: $\mlam^{(d)}_{bulk}$
      \State Using $\mlam_{bulk}^{(d)}$, apply Alg. (\ref{alg:pgreedy}), \pgreedy{}, with $\mathcal{A}_{\gmvp{}}$ to get symbol subset, $\mlam^{(d)}_{opt}$ and estimator val, $\epsilon^{(d)}_{opt}$

@@

which is then fed back into \eqn{eq:pinv3} for further refinement.

@@

\par With the conceptual tools in hand, we may proceed to constructing \gmvr{} by first defining its action, $\mathcal{A}_{\gmvr}$.

@@

    \State {\bf Input:} \{ $\mlam_{trial}$, $tol=10^{-3}$ \}

@@

    \State Calculate $\alpha^{(1)}_k$ via \eqn{eq:pinv3}. Implicitly, $n=1$.
    \State Calculate the current model prediction $g^{(1)}$ via \eqn{eq:rat4}.
    \State Calculate the model representation error, e.g.: $\epsilon^{(1)}  = |var(g^{(n)} - g^{(0)})|/var(g^{(0)})$.
    \State $done = False$
    \While { not $done$ }
      \State Calculate $\alpha^{n+1}_{k}$  via \eqn{eq:pinv3}.
      \State Calculate the current model prediction $g^{(n)}$ via \eqn{eq:rat4}.
      \State Calculate the model representation error, e.g. $\epsilon^{(n)} = |var(g^{(n)} - g^{(0)})|/var(g^{(0)})$.
      \State $done = |\epsilon^{(n)}-\epsilon^{(n-1)}| < tol$
      \State Implicitly, $n = n+1$

@@

    \State {\bf Output:} $\epsilon^{(n)}$

@@

\par The combination of \eqns{eq:pinv3} and \eqn{eq:rat4}, along with \pgreedy{} and degree tempering, results in the \gmvr{} algorithm as presented in Alg. (\ref{alg:gmvr}).
\par While not treated here, it is noted that Ref. \cite{London:2018gaq} utilizes \gmvp{} with a parameter dimension of 4.
\par In the following section we apply both \gmvp{} and \gmvr{} to the modeling of noiseless (up to roundoff error) data: the \qnm{} frequencies of Kerr \bh{s}, and the inner-products of the spherical and spheroidal harmonics.
In each case, the underlying 1D parameter in each case will be the dimensionless \bh{} spin, $\jf{}$.

@@

    \State {\bf Input:} $ \{ x, f, $max\_degree = 6$, tol \}$

@@

    \State Define, $\mlam_{bulk}$, the bulk symbol space using the n-fold cartesian inner-product of the power set of each basis symbol. This is the combined bulk for numerator and denominator symbols.
    \State Define $\mathcal{A}_{\gmvr{}}$ according to Alg. (\ref{alg:A_gmvr}).
      \State Define $\mlam_{bulk}^{(d)}$ as all symbols from $\mlam_{bulk}$ with degree less than or equal to current degree: $\mlam^{(d)}_{bulk}$
      \State Using $\mlam_{bulk}^{(d)}$, apply Alg. (\ref{alg:pgreedy}), \pgreedy{}, with $\mathcal{A}_{\gmvp{}}$ to get symbol subset, $\mlam^{(d)}_{opt}$ and estimator val, $\epsilon^{(d)}_{opt}$

@@

@@

@@

\section{Results}
\label{results}
\par We present the application of \gmvp{} and \gmvr{} to the respective modeling of \qnm{} frequencies, and harmonic mixing coefficients.
While each case is an instance of modeling on a 1D domain, we note that higher dimensional cases have been treated elsewhere \cite{London:2018gaq}.
\subsection{Modeling \qnm{} frequencies using \gmvp{}}
% Equations for QNM frequency fits
\begin{widetext}
	\input{src/cwfit_eqns}
\end{widetext}
